Real-space computation of $E$/$B$-mode maps I: Formalism, Compact Kernels, and Polarized Filaments

### 2018-06-29 articles/formalism/sections/generalizedeb.tex
Promoted generalized operators to it's own section.

%--------------------------------------------------------
%--------------------------------------------------------
\subsection{Generalized polarization operators and recovering standard power spectra}\label{sec:generalized_operators}  
With our better understanding of the radial part of the kernel for CMB polarization, we can write down generalized $E/B$-like fields that depend on a different radial function, even one that we specify to have compact support.
The spin symmetry constrains the the azimuthal part of the real space kernels to be of the form $\sim e^{\pm i2 \alpha}$.  The radial parts of the stardard operators are determined by the sum over spherical harmonics and varies as a function of the band limit. It is here that we may potentially choose alternate forms for the radial functions to suit certain kind of analysis.

>>>>

%--------------------------------------------------------
%--------------------------------------------------------
\section{Generalized polarization operators and recovering standard power spectra}\label{sec:generalized_operators}  
With our better understanding of the radial part of the kernel for CMB polarization, we can write down generalized $E/B$-like fields that depend on a different radial function, even one that we specify to have compact support.
The spin symmetry constrains the the azimuthal part of the real space kernels to be of the form $\sim e^{\pm i2 \alpha}$.  The radial parts of the stardard operators are determined by the sum over spherical harmonics and varies as a function of the band limit. It is here that we may potentially choose alternate forms for the radial functions to suit certain kind of analysis.
